Distributed Version Control Systems

### 2010-04-27 paper.tex
Quite el ", say," porque suena a demasiado informal con respecto al resto del paper.
Agregue la subseccion "Peer code review"

Merge on Git between branches is greatly improved over, say, SVN, because all the history of 
both branches is preserved over the merges.
When we make a merge we have two scenarios:
Fast-forward merge: we refer to this when the changes only was made on only one of the branches,
they are simply replayed on the other branch.
Three-way merge: When changes exists on both branches, they are merged and git will report any 
conflict and let you resolve them.

@@

%----------------------------------------------------------------------
% SECTION III: Should I use it in my project?
%----------------------------------------------------------------------
\section{Should I use it in my project?}

@@

%Explicar los casos donde resulta interesante aplicar esta herramienta. 
%También la idea es mostrar configuraciones posibles para la empresa donde 
%se vea la forma de hacer cosas que con un sistema no distribuido no sería 
%posible, o como es posible hacer lo mismo que se podía hacer con svn 
%(usando un repositorio que tenga el branch principal), de manera que 
%no te limita.

%----------------------------------------------------------------------
% SECTION IV: Then, why should I use it in my project?
%----------------------------------------------------------------------
\section{Then, why should I use it in my project?}
Does everybody need these features? Speed, offline working, 
and easyness of branching/merging are nice features even if you work simply pulling 
and pushing changes against a central repository and not every peer out there. In some 
projects and with some tools, the advantage of going distributed may not be clear. 
For starters, in many closed source projects there is no need nor desire to have anything
other than centralized repositories, and while you can use a DVCS with a centralized
repository, there may not be enough to gain to balance the cost of changing. Distributed 
versioning \emph{is} more complex, and there is a ``conceptual overhead'' in the usage 
of it, even if most of the time you can ignore most features and use just what you need 
(even for one person proyects, Git and Mercurial may be easier to use than SVN).
Centralized VCS also have their advantages, you don't need to have the whole history in your 
personal repository so you can save space, for example in Perforce you can check out only a part of the 
repository\cite{perforceclientspec} while in Git repositories can't handle millions of file 
without getting a performance hit on some operations\cite{linusgit}.

@@

%Si mi proyecto es apto para aplicar la herramienta por qué debería utilizarla en 
%vez de utilizar CVS/SVN/otros, mostrando los costos y ventajas y desventajas,
% siempre desde el punto de vista "closed source" (debatible).

>>>>

Merge on Git between branches is greatly improved over SVN, because all the history of 
both branches is preserved over the merges.
When we make a merge we have two scenarios:
Fast-forward merge: we refer to this when the changes only was made on only one of the branches,
they are simply replayed on the other branch.
Three-way merge: When changes exists on both branches, they are merged and git will report any 
conflict and let you resolve them.

@@

%----------------------------------------------------------------------
% SECTION III: Should I use it in my project?
%----------------------------------------------------------------------
%Explicar los casos donde resulta interesante aplicar esta herramienta. 
%También la idea es mostrar configuraciones posibles para la empresa donde 
%se vea la forma de hacer cosas que con un sistema no distribuido no sería 
%posible, o como es posible hacer lo mismo que se podía hacer con svn 
%(usando un repositorio que tenga el branch principal), de manera que 
%no te limita.

\section{Should I use it in my project?}

@@

\subsection{Peer code review}
If doing code review is a common practice, then using a DVCS can aid to this process. Since changes can be shared
among any workstation, the reviewer can fetch the changes from the reviewee's workstation. The reviewer might be
working on some other feature and may have it's workspace in an unstable state. But this is not a problem since the
reviewer can just clone the reviewee's repository and can have it sepparatedly from its current changes.
This also prevented them from sharing the code through a public repository, which can present some disadvantages like
a third developer using code that is not yet intended for general use.

After the review, they can push changes to some public repository for everyone to use, or the reviewer can push changes to the reviewee repository for further fixes. All of this is completely isolated from the rest of the team and with no commit history loose.

%----------------------------------------------------------------------
% SECTION IV: Then, why should I use it in my project?
%----------------------------------------------------------------------
%Si mi proyecto es apto para aplicar la herramienta por qué debería utilizarla en 
%vez de utilizar CVS/SVN/otros, mostrando los costos y ventajas y desventajas,
% siempre desde el punto de vista "closed source" (debatible).
\section{Then, why should I use it in my project?}
Does everybody need these features? Speed, offline working, 
and easyness of branching/merging are nice features even if you work simply pulling 
and pushing changes against a central repository and not every peer out there. In some 
projects and with some tools, the advantage of going distributed may not be clear. 
For starters, in many closed source projects there is no need nor desire to have anything
other than centralized repositories, and while you can use a DVCS with a centralized
repository, there may not be enough to gain to balance the cost of changing. Distributed 
versioning \emph{is} more complex, and there is a ``conceptual overhead'' in the usage 
of it, even if most of the time you can ignore most features and use just what you need 
(even for one person proyects, Git and Mercurial may be easier to use than SVN).
Centralized VCS also have their advantages, you don't need to have the whole history in your 
personal repository so you can save space, for example in Perforce you can check out only a part of the 
repository\cite{perforceclientspec} while in Git repositories can't handle millions of file 
without getting a performance hit on some operations\cite{linusgit}.

@@
